Carrier phase and amplitude estimation for phase shift keying using pilots and data

### 2012-10-30 paper.tex
added paragraph about unequal error protection for Bill

@@

Theorem~\ref{thm:consistency} defines real numbers $p$ and $d$ to represent the proportion of pilot symbols and data symbols in the limit as $L$ goes to infinity.  For Theorem~\ref{thm:normality} we need the slightly stronger condition that 
\[
\frac{\abs{P}}{L} = p + o(L^{-1/2}) \qquad \text{and} \qquad \frac{\abs{D}}{L} = d + o(L^{-1/2})
\] 
where $o(L^{-1/2})$ denotes a number such that $\sqrt{L} o(L^{-1/2})$ goes to zero as $L\rightarrow \infty$.  This stronger condition is required to prove the asymptotic normality of $\sqrt{L}\hat{m}_L$.  The next two sections give proofs for Theorems~\ref{thm:consistency}~and~\ref{thm:normality}.  The proofs make use of various lemmas.  The lemmas are proved in the appendix.

>>>>

It is straightforward to generalise the results we present here to allow data symbols with varying constellation size, i.e. varying $M$.  For example, one might give more importance to certain data symbols and use BPSK ($M=2$) for these, but QPSK ($M=4$) for other less important symbols.  This is related to what is called \emph{unequal error protection} in the literature~\cite{Aydinlik_turbo_uep_2008,Sandberg_uep_ldpc_2010}.  To keep our ideas and notation focused we don't consider this further here.

@@

Theorem~\ref{thm:consistency} defines real numbers $p$ and $d$ to represent the proportion of pilot symbols and data symbols in the limit as $L$ goes to infinity.  For Theorem~\ref{thm:normality} we need the slightly stronger condition that 
\[
\frac{\abs{P}}{L} = p + o(L^{-1/2}) \qquad \text{and} \qquad \frac{\abs{D}}{L} = d + o(L^{-1/2})
\] 
where $o(L^{-1/2})$ denotes a number such that $\sqrt{L} o(L^{-1/2})$ goes to zero as $L\rightarrow \infty$.  This stronger condition is required to prove the asymptotic normality of $\sqrt{L}\hat{m}_L$.

The next two sections give proofs for Theorems~\ref{thm:consistency}~and~\ref{thm:normality}.  The proofs make use of various lemmas.  The lemmas are proved in the appendix.
